### 2021-05-04 initial/notes.tex
can't decide on color but technically have a draft

>>>>

\subsubsection{Physical Numbers}

We focus on the USP regime. In the notation of the paper, we need
\begin{align}
    1
        &\approx \frac{2n / \Omega_{\rm s} - \cos \theta
            }{\abs{g}t_{\rm a}\sin I}.
\end{align}
One tricky thing about this calculation is that $\eta$ depends on $\Omega_{\rm
s}$ which depends on $\cos \theta$ which depends on $\eta$:
\begin{align}
    \eta &= \eta_{\rm sync} \frac{n}{\Omega_{\rm s}},\\
    \frac{n}{\Omega_{\rm s}} &= \frac{1 + \cos^2\theta}{2 \cos \theta},\\
    \cos \theta &\approx \frac{\eta \cos I}{1 + \eta \sin I}.
\end{align}
This requires that
\begin{align}
    \frac{\eta}{\eta_{\rm sync}} &\approx \frac{1 + \eta \sin I
        }{2\eta \cos I},\\
    2\eta^2 \cos I &\approx \eta_{\rm sync} + \eta_{\rm sync}\eta \sin I,\\
    \eta &= \frac{\eta_{\rm sync}\sin I + \sqrt{
        \eta_{\rm sync}^2 \sin^2 I + 8\cos I \eta_{\rm sync}}}{
            4 \cos I}.
\end{align}
It proves sufficient to use the simpler form of this:
\begin{align}
    \eta &\approx \sqrt{\frac{\eta_{\rm sync}}{2\cos I}},\\
    t_{\rm a, c} &= \frac{2n / \Omega_{\rm s}}{\abs{g}\sin I},\\
        &= \frac{2}{\abs{g}\sin I\sqrt{2\eta_{\rm sync} \cos I}}.
\end{align}
Thus, we can continue to evaluate laboriously:
\begin{align}
    \frac{1}{t_{\rm s, c}} &= \abs{g}\sin I \sqrt{\frac{\eta_{\rm sync} \cos
        I}{2}},\\
    g &= \frac{3m_p}{4M_{\star}}\p{\frac{a}{a_{\rm p}}}^3 n,\\
    \frac{1}{t_{\rm s}} &= \frac{1}{4k}\frac{3k_2}{Q} \frac{M_{\star}}{m}
        \p{\frac{R}{a}}^3 n,\\
    \eta_{\rm sync} &= \s{\frac{3m_p}{4M_{\star}}\p{\frac{a}{a_{\rm p}}}^3 n}
        \Bigg/ \s{\frac{3k_q}{2k} \frac{M_\star}{m}\p{\frac{R}{a}}^3 n},\\
        &= \frac{m_pm}{2M_\star^2}\p{\frac{a}{a_{\rm p}}}^3
            \p{\frac{a}{R}}^3,\\
    \frac{1}{4k}\frac{3k_2}{Q}\frac{M_\star}{m}\p{\frac{R}{a}}^3
        &= \frac{3m_{\rm p}}{4M_{\star}}\p{\frac{a}{a_{\rm p}}}^3
            \sin I \sqrt{\frac{\cos I}{2}}
            \sqrt{\frac{m_pm}{2M_\star^2}\p{\frac{a}{a_{\rm p}}}^3
                \p{\frac{a}{R}}^3 \frac{k}{k_q}},\\
    a^9 &= 4\frac{2k_2}{Q} \frac{M_\star^3}{(mm_{\rm p})^{3/2}}
        \p{Ra_{\rm p}}^{9/2}\frac{1}{\sin I \sqrt{\cos I}}
        \p{\frac{k}{k_{\rm q}}}^{-1/2},\\
% (4 * 1e-3 * (Msun / (8 Mearth))^3 * ((2 Rearth) * (0.05 AU))^(9/2))^(1/9) / (1 AU)
% = 0.0387
    a_{\rm break} &\approx 0.038 \;\mathrm{AU}
        \p{\frac{2k_2/Q}{10^{-3}}}^{1/9}
        \p{\frac{M_\star}{M_{\odot}}}^{1/3}
        \p{\frac{8M_{\oplus}}{m}}^{-1/3}
        \p{\frac{R}{2R_{\oplus}}}^{1/2}
        \p{\frac{a_{\rm p}}{0.05\;\mathrm{AU}}}^{1/2}
        \p{\frac{1}{\sin I \sqrt{\cos I}}}^{1/9},\\
% ((8 Mearth)^2 / (Msun)^2) / 2 * (1.3)^(-2) * ((0.035 AU) / (2 Rearth))^3
% = 0.011845
    \eta_{\rm sync} &= \frac{m_pm}{2M_\star^2}\p{\frac{a}{a_{\rm p}}}^3
            \p{\frac{a}{R}}^3,\\
        &= 0.012 \p{\frac{k}{k_{\rm q}}}
                \p{\frac{m}{8 M_{\oplus}}}^2
                \p{\frac{M_\star}{M_{\odot}}}^{-2}
            \p{\frac{a}{0.035 \;\mathrm{AU}}}^{3}
                \p{\frac{P_{j + 1} / P_j}{1.5}}^{-2}
                \p{\frac{R}{2R_{\oplus}}}^{-3}.
\end{align}
For WASP-12b, we instead can solve for
\begin{align}
    \frac{m_{\rm p}^{3/2}}{a_{\rm p}^{9/2}}
        &= 4\frac{2k_2}{Q} \frac{M_\star^3}{m^{3/2}}
        \p{\frac{R}{a^2}}^{9/2}\frac{1}{\sin I \sqrt{\cos I}}
        \p{\frac{k}{k_{\rm q}}}^{-1/2},\\
    \frac{m_{\rm p}}{a_{\rm p}^3}
        &\gtrsim 0.0002 \;\mathrm{kg/m^3}
            \p{\frac{2k_2/Q}{10^{-7}}}^{2/3}
            \p{\frac{M_\star}{1.36 M_{\odot}}}^{2}
            \p{\frac{m}{1.41 M_{\rm J}}}^{-1}
            \p{\frac{R}{1.89R_{\rm J}}}^{3}
            \p{\frac{a}{0.023\;\mathrm{AU}}}^{-6}
            \p{\frac{1}{\sin I \sqrt{\cos I}}}^{2/3}.
\end{align}
If WASP-12b is in tCE2, then this must be satisfied by the perturber.

However, recall here that $I$ should really be the angle between $\bm{L}$ and
$\bm{L}_{\rm tot} = \bm{L} + \bm{L}_{\rm out}$. When $L \gg L_{\rm out}$ as in
this case, we must reduce $\sin I = (L_{\rm out} / L) \sin I_{\rm tot}$, where
$I_{\rm tot}$ is the mutual inclination between the orbits. For circular orbits
and small $I_{\rm tot}$, we can write
\begin{align}
    \frac{L_{\rm out}}{L} \approx{}& \frac{m_{\rm p}}{m}
            \sqrt{\frac{a_{\rm p}}{a}}\nonumber\\
        &= 0.132,\\
    \p{\frac{m_{\rm p}}{40 M_{\oplus}}}\p{\frac{a_{\rm
        p}}{0.05\;\mathrm{AU}}}^{-3} \gtrsim {}& 0.4
            \p{\frac{2k_2/Q}{10^{-7}}}^{2/3}
            \p{\frac{M_\star}{1.36 M_{\odot}}}^{2}
            \p{\frac{m}{1.41 M_{\rm J}}}^{-1}
            \p{\frac{R}{1.89R_{\rm J}}}^{3}\nonumber\\
        &\times \p{\frac{a}{0.023\;\mathrm{AU}}}^{-6}
            \p{\frac{m}{m_{\rm p}} \sqrt{\frac{a}{a_{\rm p}}}
                \frac{1}{\sin I_{\rm tot}}}^{2/3},\\
    \p{\frac{m_{\rm p}}{40 M_{\oplus}}}^{5/3}\p{\frac{a_{\rm
        p}}{0.05\;\mathrm{AU}}}^{-8/3} \gtrsim {}& 1.5
            \p{\frac{2k_2/Q}{10^{-7}}}^{2/3}
            \p{\frac{M_\star}{1.36 M_{\odot}}}^{2}
            \p{\frac{m}{1.41 M_{\rm J}}}^{-1}
            \p{\frac{R}{1.89R_{\rm J}}}^{3}\nonumber\\
        &\times \p{\frac{a}{0.023\;\mathrm{AU}}}^{-6}
            \p{\frac{1}{\sin I_{\rm tot}}}^{2/3}.
\end{align}

What is the corresponding RV signal of such a planet? The RV signal in the star
is given as a velocity, which is just $n_{\rm p} \times a_{\rm p}\frac{m_{\rm
p}}{M_{\star}}$. Including the projection effect by an angle $i$, we should find
that
\begin{align}
    \text{RV semi-amplitude} &\approx
            n_{\rm p}a_{\rm p}\frac{m_{\rm p}}{M_{\star}} \sin i,\\
        &\approx 10\;\mathrm{m/s} \frac{\sin i}{1/\sqrt{2}}
\end{align}
This is in agreement with Fig 3 of Millholland's plot.
